\documentclass[11pt, a4paper]{article}

\usepackage{amsmath}
\usepackage{url}

\title{Intelligent autonomous weapons}
\author{Daniel Gustafsson}
\date{November 2021}

\begin{document}
\maketitle

\section{Should autonomous lethal weapons be banned?}
In this section I present three arguments and counter arguments for autonomous lethal weapons.
\subsection{Argument 1}
\textbf{For :} Using autonomous lethal weapons as a substitute for human military personnel will reduce human casualties in combat zones.

\vspace{2mm}\noindent\textbf{Against :} This is only true in certain scenarios. Consider a battle situation where neither side is using
human military personnel but only autonomous lethal weapons. Who will be targeted by these weapons? If no combatants exists, the weapons
are either useless or will target civilians where the latter is probably more likely.

\subsection{Argument 2}
\textbf{For :} A machines judgment will never be clouded by emotion as a humans will. A machine can't get angry and act on impulse etc.

\vspace{2mm}\noindent\textbf{Against :} It is correct to assume a machine do not posses human emotions and will not act up on them.
This also means that a machine sent out to kill or destroy will not stop because of some unforeseen circumstance that would make any
human think twice. 

Consider a scenario where a terrorist leader is found and some state with access to autonomous lethal weapons decides
to kill him. Some autonomous drone carrying an explosive is sent out, the terrorist leader hears about this somehow and hides in a 
hospital building. A human controlled weapon would certainly think twice about sending an explosive device into a hospital and might
decide to put the attack on hold. An autonomous weapon will only follow its programming, if an event such as this is not considered
during manufacturing, the weapon will carry on with its mission.

\subsection{Argument 3}
\textbf{For :} Using autonomous lethal weapons, a states military can reduce the human personnel needs significantly. This could lead to many
states removing mandatory military service. This could also lead to a reduction in military spending and thus enable the state to
fund other projects such as health care.

\vspace{2mm}\noindent\textbf{Against :} A military force being run by fewer humans is not necessarily a good thing. What is stopping a
small minority of people who controls the autonomous lethal weapons from declaring themselves rulers of a state? Autonomous lethal weapons
would increase the power of the few and make a revolt against an evil government increasingly impossible.

\subsection{Discussion}
If it isn't obvious from the arguments/counter arguments, I am fully against the manufacturing of autonomous lethal weapons.
I do however believe they are inevitable in the coming few years. 

In the Youtube clip Slaughterbots\cite{slaughterbots},
tiny autonomous drones with cameras and facial recognition technology armed with small explosive devices are pictured.
The video paints up a dystopian future where these drones are used to control the public opinion and kill ethical minorities.
I don't know if these drones exist yet but all the tech to create them is readily available.

I think that banning autonomous lethal weapons is essential for the future of humanity and that the only ethical reason to research more about
them is to find an effective defense against them.

\section{Moral responsibility of an engineer/computer scientist}
In the scenario described in the assignment, I would advice my classmate to carefully consider the ethics of this possibility. I don't
think it is up to me to decide what is best for my classmate. It would be easy for me to tell my classmate that it would be unethical to
accept the offer, but on the other hand, we are only students and hardly considered experts in our field yet. What damage could we possibly
do by participating in this project that the company would still complete whether I or another student chooses not to partake. 

I think it
would be hard not to accept the offer if I received it myself. It also feels much better that its a Swedish company because of our supposed
high morale standard. I don't think it is correct to think this way but I am just confessing that it would be hard not to in this scenario.

\bibliographystyle{amsplain}
\bibliography{hw8.bib}

\end{document}
